---
title: "Hate Crimes in the United States (2019-2020)"
author: "Anne Clark, Sylvia Duan, Amrith Gandham,  Mahir Krishnan"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
source("../source/summary.R")
```

There were **`r formatC(total_hate_crimes_2019_20, format="d", big.mark=",")`** hate crimes in 2019 and 2020. **`r formatC(total_hate_crimes_2019, format="d", big.mark=",")`** of these occurred in 2019 and **`r formatC(total_hate_crimes_2020, format="d", big.mark=",")`** of these occurred in 2020.  The most common hate crime in 2019 was **`r most_common_2019`**, composing **`r round(percentage_most_common_2019,digits = 3)*100`%** of all hate crimes.  The most common hate crime in 2020 was **`r most_common_2020`**, composing **`r round(percentage_most_common_2020,digits = 3)*100`%** of all hate crimes.

## Table: Hate Crimes per state

```{r, include=FALSE}
source("../source/table.r")
```

```{r, echo=FALSE}
library(knitr)
kable(aggregate_table)
```

This table 

## Graphs

### Figure 1: Hate Crime Count vs. Income Per Capita

```{r, include=FALSE}
source("../source/chart_1.r")
```

```{r echo=FALSE}
income_vs_counts_2020
```



### Figure 2: Top Ten Hate Crime Biases (2019-2020)

```{r, include=FALSE}
source("../source/chart_2.r")
```



```{r, echo=FALSE}
plot
```

This chart shows the top ten hate crime biases in these two years and how many of each there are. This was chosen because it shows which groups are most disproportionately affected by hate crime.  An insight that can be pulled from this data is the over representation of anti-African-American hate crime in this data, despite only making up about 13% of the US population, African Americans are the most targeted group by hate crime, and about three times more common than anti-White hate crimes, despite white people making a majority of the population.  This puts on display the extent of modern racial tensions in the United States.

### Figure 3: Line Graph of Hate crimes (2019-2020)



